### 2024-04-04 paper/paper.qmd
rough draft for the introduction paragraph

---
title: "Gamification Effectiveness on Education"
author: 
  - Sachin Chhikara
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
```

# Introduction

Games have been part of human history for a long time and are loved by many young and old. The design behind why game are so fun have investigated in recent time and how to apply those element that are fun and to apply them to other fields, this is known as gamification. Gamification is used in fields such as enterprise, sales, lifestyle and education. In this paper we will focusing on application of education, we be using data from Duolingu, training model and making inference off, real life application of gamification to an individual productive.

# Data {#sec-data}

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

\newpage

# References
---
nocite: '@*'
---

### 2024-04-08 scripts/02-data_cleaning.R
added raw clean data and a script to clean it

@@ -1,7 +1,7 @@
 #### Preamble ####
 # Purpose: Cleans the raw data
 # Author: Sachin Chhikara
-# Date: 26 March 2024 
+# Date: 8 April 2024 
 # Contact: sachin.chhikarar@utoronto.ca
 # License: MIT
 
@@ -10,18 +10,20 @@ library(arrow)
 library(tidyverse)
 
 #### Clean data ####
-raw_data <- read_csv("data/raw_data/raw_data.csv")
+raw_data <- read_csv("data/raw_data/1-s2.0-S2352340917300173-mmc2.csv")
+
 
 cleaned_data <-
   raw_data |>
-  janitor::clean_names() |>
-  select(-timestamp) |>
-  rename(c(certainty = how_certain_about_your_guess_are_you,
-           outcome = what_was_the_outcome)) |> 
-  mutate(
-    outcome = if_else(outcome == "Guessed right",
-                      1,
-                      0))
+  select(-Age) |>
+  mutate(Group = case_when(
+    Group == 0 ~ "Control group",
+    Group == 1 ~ "Educational game",
+    Group == 2 ~ "Gamification plugin",
+    Group == 3 ~ "Social networking website",
+    Group == 4 ~ "Social gamified networking website"
+  ))
+
 
 
 #### Save data ####

### 2024-04-08 paper/paper.qmd
rough notes about the outline of the paper

@@
 In this paper we will focusing on application of education, we be using data from Duolingu, training model and making inference off, real life application of gamification to an individual productive.
+
+In this paper, we are doing replication of a study ...
+, which has a control and treatment where the treatment is applied gamification, while the control is using an ordinary education system.
+Yeah there benefits, but there are downside when comes to how the gamification as it might discourage learning.
+Furthermore, an wide use application of gamification is a language learning app called Duolingo, which has ...
+active users and this app learning is recognized in certain Universities as legitimate English learning.So we examine game design that are use.
+Ways to apply gamification in daily lives, like this app called Habitica: Gamify your tasks.
 

### 2024-04-08 scripts/02-data_cleaning.R
use the full name instead of abbreviation for the gender column

@@ -22,7 +22,9 @@ cleaned_data <-
     Group == 2 ~ "Gamification plugin",
     Group == 3 ~ "Social networking website",
     Group == 4 ~ "Social gamified networking website"
-  ))
+  ),
+  Gender = case_when(Gender == "M" ~ "Male", Gender == "F" ~ "Female")
+  )
 
 
 

### 2024-04-08 scripts/04-model.R
rough draft for the model created

@@ -10,28 +10,25 @@
 library(arrow)
 library(tidyverse)
 library(rstanarm)
+library(modelsummary)
 
 #### Read data ####
 analysis_data <- read_parquet(file = "data/analysis_data/analysis_data.parquet")
 
-analysis_data |>
-  ggplot(aes(x = certainty, y = outcome)) +
-  geom_jitter(height = 0)
-
 
 ### Model data ####
 first_model <-
-  stan_glm(
-    formula = outcome ~ certainty,
+  stan_glm( 
+    formula = FinalExamination ~ Group,
     data = analysis_data,
-    family = binomial(link = "logit"),
+    family = gaussian(),
     prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
     prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
     prior_aux = exponential(rate = 1, autoscale = TRUE),
     seed = 853
   )
 
-summary(first_model)
+modelsummary(first_model)
 
 #### Save model ####
 saveRDS(

### 2024-04-08 scripts/02-data_cleaning.R
removed missing data

@@ -24,7 +24,9 @@ cleaned_data <-
     Group == 4 ~ "Social gamified networking website"
   ),
   Gender = case_when(Gender == "M" ~ "Male", Gender == "F" ~ "Female")
-  )
+  ) |>
+  tidyr::drop_na()
+  
 
 
 

### 2024-04-08 scripts/03-test_data.R
added tests for the analysis data

@@ -1,15 +1,105 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Run tests on the analysis data
+# Author: Sachin Chhikara
+# Date: 8 April 2024 
+# Contact: sachin.chhikarar@utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
 
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
+library(arrow)
+
+analysis_data <- read_parquet("data/analysis_data/analysis_data.parquet")
+
+##Helper functions
+is_column_of_type <- function(dataframe, column_name, datatype) {
+  column_class <- class(dataframe[[column_name]])
+  return(datatype %in% column_class)
+}
+
+check_numeric_columns <- function(dataframe, column_names) {
+  for (col in column_names) {
+    if (is_column_of_type(dataframe, col, "numeric")) {
+      message(paste(col, ": All values are numeric"))
+    } else {
+      message(paste(col, "Error: Not all values are numeric"))
+    }
+  }
+}
+
+check_gender_values <- function(dataframe, column_name, expected_values) {
+  column_values <- dataframe[[column_name]]
+  if (all(column_values %in% expected_values)) {
+    message(paste(column_name, ": All values are valid"))
+  } else {
+    message(paste(column_name, "Error: Some values are not valid"))
+  }
+}
+
+check_values_between_0_and_100 <- function(column_values_list) {
+  for (i in seq_along(column_values_list)) {
+    column_values <- column_values_list[[i]][[1]]
+    column_name <- column_values_list[[i]][[2]]
+    if (all(column_values >= 0 & column_values <= 100)) {
+      message(paste(column_name, ": The values are between 0 and 100 as expected"))
+    } else {
+      message(paste(column_name, "Error: There is an inappropriate value in this dataset. Double check that the dataset was modified incorrectly or remove that value from the dataset if necessary"))
+    }
+  }
+}
 
 #### Test data ####
+#1.Proper datatype is used for each column 
+if (is_column_of_type(analysis_data, "Group", "character")) {
[…]

### 2024-04-09 paper/paper.qmd
added references to the paper I am using and other common libraries I am been using

@@
 library(palmerpenguins)
+library(arrow)
 ```
@@
 
-analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))
+analysis_data <- read_parquet(here::here("data/analysis_data/analysis_data.parquet"))
 
-analysis_data |> 
-  ggplot(aes(x = width, y = length)) +
-  geom_point(alpha = 0.8) +
-  theme_minimal() +
-  labs(x = "Wing width (mm)",
-       y = "Wing length (mm)")
 ```

### 2024-04-12 scripts/99-replications.R
finished replication of the tables

@@ -1,19 +1,79 @@
 #### Preamble ####
-# Purpose: Replicated graphs from... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Models whether we guess right based off of our confidence
+# Author: Sachin Chhikara
+# Date: 11 April 2024 
+# Contact: sachin.chhikarar@utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
-
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
+library(arrow)
+library(knitr)
+library(kableExtra)
 
 #### Load data ####
-# [...ADD CODE HERE...]
+analysis_data <- read_parquet(file = "data/analysis_data/analysis_data.parquet")
+
+#number of people in each group
+value_counts <- table(analysis_data$Group)
+
+
+### Helper Functions ###
+summarize_column_stats <- function(data, column_name) {
+  stats <- data %>%
+    group_by(Group) %>%
+    summarise(
+      mean = round(mean({{column_name}}), 2),
+      sd = round(sd({{column_name}}), 2),
+      se = round(sd({{column_name}})/sqrt(n()), 2)
+    )
+  
+  return(stats)
+}
+
+
+#### Tables ####
+
+# Table 2
+#pretest stats
+w_stats <- summarize_column_stats(analysis_data, WordProcPretest)
+s_stats <- summarize_column_stats(analysis_data, SpreadsheetsPretest)
+p_stats <- summarize_column_stats(analysis_data, PresentationPretest)
+d_stats <- summarize_column_stats(analysis_data, DatabasesPretest)
+  
+
+data <- data.frame(
+  Evaluation_item = rep(c("Word Processing", "Spreadsheets", "Presentations", "Databases"), each = 5),
+  Group = rep(c("Control", "Ed. Game", "Gamification", "Social", "Social Gamif."), 4),
+  N = rep(value_counts, 4),
+  Mean = c(w_stats$mean, s_stats$mean, p_stats$mean, d_stats$mean),
[…]

### 2024-04-12 scripts/99-replications.R
replicate figures

@@ -70,10 +70,14 @@ data2 <- data.frame(
 )
 
 ### Figures ###
-
 #Figure 5
 
+
 #Figure 6
-
-
+ggplot(analysis_data, aes(x = Group, y = FinalExamination, color = Group)) +
+  geom_boxplot() +
+  geom_point() +
+  geom_jitter(alpha = 0.3, width = 0.15, height = 0) +
+  labs(x = "Group Type", y = "Final Examination Grade", title = "Scatterplot of Grades by Group Type") +
+  theme(axis.text.x = element_blank())
 

### 2024-04-12 scripts/99-replications.R
added png of the figures created

@@ -10,6 +10,7 @@ library(tidyverse)
 library(arrow)
 library(knitr)
 library(kableExtra)
+library(gridExtra)
 
 #### Load data ####
 analysis_data <- read_parquet(file = "data/analysis_data/analysis_data.parquet")
@@ -71,13 +72,43 @@ data2 <- data.frame(
 
 ### Figures ###
 #Figure 5
-
-
-#Figure 6
-ggplot(analysis_data, aes(x = Group, y = FinalExamination, color = Group)) +
+plot1 <- ggplot(analysis_data, aes(x = Group, y = WordProcPosttest, color = Group)) +
   geom_boxplot() +
   geom_point() +
   geom_jitter(alpha = 0.3, width = 0.15, height = 0) +
-  labs(x = "Group Type", y = "Final Examination Grade", title = "Scatterplot of Grades by Group Type") +
+  labs(x = "Group Type", y = "Word Processing") +
   theme(axis.text.x = element_blank())
 
+plot2 <- ggplot(analysis_data, aes(x = Group, y = SpreadsheetsPosttest, color = Group)) +
+  geom_boxplot() +
+  geom_point() +
+  geom_jitter(alpha = 0.3, width = 0.15, height = 0) +
+  labs(x = "Group Type", y = "Presentations") +
+  theme(axis.text.x = element_blank())
+
+plot3 <- ggplot(analysis_data, aes(x = Group, y = PresentationPosttest, color = Group)) +
+  geom_boxplot() +
+  geom_point() +
+  geom_jitter(alpha = 0.3, width = 0.15, height = 0) +
+  labs(x = "Group Type", y = "Word Processing") +
+  theme(axis.text.x = element_blank())
+
+plot4 <- ggplot(analysis_data, aes(x = Group, y = DatabasesPosttest, color = Group)) +
+  geom_boxplot() +
+  geom_point() +
+  geom_jitter(alpha = 0.3, width = 0.15, height = 0) +
+  labs(x = "Group Type", y = "Databases") +
+  theme(axis.text.x = element_blank())
+
+fig5 <- grid.arrange(plot1, plot2, plot3, plot4, nrow = 2, ncol = 2)
+ggsave("other/figures/figure5.png", width = 10, height = 8, fig5) 
+
+#Figure 6
+fig6 <- ggplot(analysis_data, aes(x = Group, y = FinalExamination, color = Group)) +
+  geom_boxplot() +
+  geom_point() +
[…]

### 2024-04-12 scripts/04-model.R
created models

@@ -1,10 +1,9 @@
 #### Preamble ####
-# Purpose: Models whether we guess right based off of our confidence
+# Purpose: Models the assessment given to the student against the group they were in
 # Author: Sachin Chhikara
-# Date: 26 March 2024 
+# Date: 12 April 2024 
 # Contact: sachin.chhikarar@utoronto.ca
 # License: MIT
-# Pre-requisites: 02-data_cleaning.R
 
 #### Workspace setup ####
 library(arrow)
@@ -15,20 +14,51 @@ library(modelsummary)
 #### Read data ####
 analysis_data <- read_parquet(file = "data/analysis_data/analysis_data.parquet")
 
-
 ### Model data ####
-first_model <-
+Word_model <-
+  stan_glm( 
+    formula = WordProcPosttest ~ Group,
+    data = analysis_data,
+    family = gaussian(),
+    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
+    seed = 849
+  )
+
+modelsummary(Word_model)
+
+Spreadsheet_model <-
+  stan_glm( 
+    formula = SpreadsheetsPosttest ~ Group,
+    data = analysis_data,
+    family = gaussian(),
+    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
+    seed = 849
+  )
+
+modelsummary(Spreadsheet_model)
+
+Database_model <-
+  stan_glm( 
+    formula = DatabasesPosttest ~ Group,
+    data = analysis_data,
+    family = gaussian(),
+    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
+    seed = 849
+  )
+
+modelsummary(Database_model)
+
+
+FinalExam_model <-
   stan_glm( 
     formula = FinalExamination ~ Group,
     data = analysis_data,
     family = gaussian(),
     prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
     seed = 853
   )
 
-modelsummary(first_model)
+modelsummary(FinalExam_model)
 
 #### Save model ####
 saveRDS(

### 2024-04-14 paper/paper.qmd
worked on the first few paragraphs of the data section

@@
 
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
+The original study used 379 undergraduates for their experiments and there were randomly assigned into 5 groups Control, Educational game, Gamification Plugin, Social networking website, Social gamified networking website.
+The experiment was carried out on 10-week first year undergraduate class called ‘Qualification for ICT Users’ with hybrid learning.
+This course is an introduction to basic computing concepts such as word processing, spreadsheets, presentations and databases.
+There is an assignment for each of these four concepts which focus on testing practical skills.
+While, the final examination is cumulative and focus on testing conceptual knowledge.
+
+Students have lecture every two weeks and must work independently rest of the work to learn then material.
+Supplementary learning material was provided such as videos and communication tools in learning material platform.
+
+The control group just use what was mention above.
+Educational game used was called Ribbonhero offered by Microsoft as as free download to download Software, and player plays as virtual character Clippy and must overcome six challenges with increasing difficulty.
+Gamification plugin (fig 1) is integrated in the institutional management system where there are challenges, trophies/badges and a leader board.
+Social Networking website was run on a open source engine, Elgg (fig 2) and it functions very similar to social media where students can share their thoughts, make friends and discuss the material in class.
+Social gamified networking website use the same engine as the previous group and having similar features to Gamification plugin(fig 3).
+A summary of the groups features and potential benefits (fig 4).
+The study highlights that the educational game is not necessarily aligned with the learning goals, while the gamification used in this study was.
 
@@
 
+```{=tex}
 \begin{align} 
@@
 \end{align}
-
+```
 We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
@@
 
-# Appendix {-}
+# Appendix {.unnumbered}
 
@@
 # References
+
 ---

### 2024-04-15 paper/paper.qmd
added a paragraph on the data cleaning prodecure

@@
 
-# Data {#sec-data}
+# Data
+
+## 2.1 Background of Original Study
 
@@
 The study highlights that the educational game is not necessarily aligned with the learning goals, while the gamification used in this study was.
+
+## 2.2 Data Cleaning Procedure
+
+For our replication, we drop 20 rows of data from the original dataset provided since those rows contained missing data on grades of some assessments and final examination.
+The age row was removed since in the original study it mention that there age range for each group but in the dataset provided they made every value in that column to 19 since that the average age in the study.
 
@@
 
-## First discussion point {#sec-first-point}
+## First discussion point
 
@@
 
-# Model details {#sec-model-details}
+# Model details
 

### 2024-04-15 paper/paper.qmd
mention sample size for each group
forget to include this in the last commit lol

@@
 
-The original study used 379 undergraduates for their experiments and there were randomly assigned into 5 groups Control, Educational game, Gamification Plugin, Social networking website, Social gamified networking website.
+The original study used 379 undergraduates for their experiments and there were randomly assigned into 5 groups Control(N=76), Educational game(N=75), Gamification Plugin(N=77), Social networking website(N=75), Social gamified networking website(N=76).
 The experiment was carried out on 10-week first year undergraduate class called ‘Qualification for ICT Users’ with hybrid learning.
@@
 The age row was removed since in the original study it mention that there age range for each group but in the dataset provided they made every value in that column to 19 since that the average age in the study.
+To summarize, the size of the dataset we use in this replication is N = 359 (Control=75, Game=66, Plugin=73, Social Network=74, Social Gamification=71)
+
+This dataset was chosen since my many studies in gamification don't have easy access to their datasets and this dataset includes control and treatment group which is useful for examining the difference between a traditonal education system and gamification.
+
+## 2.4 Data Analysis
 

### 2024-04-15 paper/paper.qmd
added figures to Methodology section and cross references

@@
 
-## 2.1 Background of Original Study
+## Data Source
+
+## Methodology
 
@@
 Educational game used was called Ribbonhero offered by Microsoft as as free download to download Software, and player plays as virtual character Clippy and must overcome six challenges with increasing difficulty.
-Gamification plugin (fig 1) is integrated in the institutional management system where there are challenges, trophies/badges and a leader board.
-Social Networking website was run on a open source engine, Elgg (fig 2) and it functions very similar to social media where students can share their thoughts, make friends and discuss the material in class.
-Social gamified networking website use the same engine as the previous group and having similar features to Gamification plugin(fig 3).
-A summary of the groups features and potential benefits (fig 4).
+Gamification plugin (@fig-Gamification-plugin) is integrated in the institutional management system where there are challenges, trophies/badges and a leader board.
+Social Networking website was run on a open source engine, Elgg (@fig-social_network) and it functions very similar to social media where students can share their thoughts, make friends and discuss the material in class.
+Social gamified networking website use the same engine as the previous group and having similar features to Gamification plugin(@fig-social_gamification).
+A summary of the groups features and potential benefits (table 1).
 The study highlights that the educational game is not necessarily aligned with the learning goals, while the gamification used in this study was.
 
-## 2.2 Data Cleaning Procedure
+```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| label: fig-Gamification-plugin
+#| fig-cap: "Gamifcation Plugin. Leaderboard and challenges."
+knitr::include_graphics(file.path(here::here(),"other/figures/figure1.jpg")) 
+```
+```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| label: fig-social_network
+#| fig-cap: "Social Networking Website."
+knitr::include_graphics(file.path(here::here(),"other/figures/figure2.jpg")) 
+```
+```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| label: fig-social_gamification
+#| fig-cap: "Social gamification website: Gamification tools (left), dashboard (top-right) & leaderboard (bottom-right)."
+knitr::include_graphics(file.path(here::here(),"other/figures/figure3.jpg")) 
+```
+```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| label: fig-social_gamification
+#| table-cap: "Social gamification website: Gamification tools (left), dashboard (top-right) & leaderboard (bottom-right)."
+knitr::include_graphics(file.path(here::here(),"other/tables/table1.jpg")) 
+```
+
+## Data Cleaning Procedure
 
@@
 The age row was removed since in the original study it mention that there age range for each group but in the dataset provided they made every value in that column to 19 since that the average age in the study.
-To summarize, the size of the dataset we use in this replication is N = 359 (Control=75, Game=66, Plugin=73, Social Network=74, Social Gamification=71)
+To summarize, the size of the dataset we use in this replication is N = 359(Control=75, Game=66, Plugin=73, Social Network=74, Social Gamification=71).
 
-This dataset was chosen since my many studies in gamification don't have easy access to their datasets and this dataset includes control and treatment group which is useful for examining the difference between a traditonal education system and gamification.
+This dataset was chosen since my many studies in gamification don't have easy access to their datasets.
+In addition, this dataset includes control and treatment group which is useful for examining the difference between a traditional education system and gamification.
 
-## 2.4 Data Analysis
+## Data Visualization
 

### 2024-04-16 paper/paper.qmd
save copy of the tables and rendering in the paper

@@
 Social gamified networking website use the same engine as the previous group and having similar features to Gamification plugin(@fig-social_gamification).
-A summary of the groups features and potential benefits (table 1).
+A summary of the groups features and potential benefits(@tb-summary-group).
 The study highlights that the educational game is not necessarily aligned with the learning goals, while the gamification used in this study was.
@@
 ```{r}
+#| eval: true
 #| echo: false
-#| eval: true
+#| message: false
 #| warning: false
-#| message: false
-#| label: fig-social_gamification
-#| table-cap: "Social gamification website: Gamification tools (left), dashboard (top-right) & leaderboard (bottom-right)."
-knitr::include_graphics(file.path(here::here(),"other/tables/table1.jpg")) 
+#| label: tb-summary-group
+#| tbl-cap: "Summary of the groups used, their features and potential benefits."
+
+htmltools::includeHTML(file.path(here::here(),"other/tables/table1.html"))
 ```
@@
 ```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
+#| eval: true
 #| echo: false
+#| message: false
+#| warning: false
+#| label: tb-pretest
+#| tbl-cap: "The results of the pretest."
 
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = "none") +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
+htmltools::includeHTML(file.path(here::here(),"other/tables/table2.html"))
 ```
 
-Talk more about it.
+```{r}
+#| eval: true
+#| echo: false
+#| message: false
+#| warning: false
+#| label: tb-posttest
+#| tbl-cap: "The results of the posttest."
+
+htmltools::includeHTML(file.path(here::here(),"other/tables/table3.html"))
+```
 

### 2024-04-16 scripts/99-replications.R

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Models whether we guess right based off of our confidence
+# Purpose: Replicates the tables and figures used in original study
 # Author: Sachin Chhikara
 # Date: 11 April 2024 
 # Contact: sachin.chhikarar@utoronto.ca
@@ -34,6 +34,20 @@ summarize_column_stats <- function(data, column_name) {
 
 
 #### Tables ####
+# Table 1
+
+# Note: This table was used in original study, but the table code was not provided.
+# So replicate it, we took a screenshot of the table and told chatgpt to create this table.
+table1 <- data.frame(
+  Instrument = c("Educational game", "Gamification plugin", "Social networking website", "Social gamification website"),
+  Features = c("Challenges, levels, points, narrative", "Trophies, badges, challenges, leaderboard", "Blogging, questions & answers, liking, friends, built-in twitter, dashboard", "Blogging, questions & answers, liking, friends, built-in twitter, dashboard, challenges, points, achievements, virtual currency, shop, external rewarding, personalization (status/visibility), peer review"),
+  `Approach & targeted benefits` = c("Not aligned with learning objectives Independent work & exploration of students", "Competition-driven Motivate participation through comparison with peers", "Cooperation and communication among participants. Boost participation, collaborative work & community building Promote student-driven discussion", "Competition and cooperation Boost participation, collaborative work & community building Motivate participation through comparison with peers Social interaction affords additional means to motivate participation and engagement Addressing needs of different students (player types) and widen participation")
+)
+
+# Saves the table to an html file
+table_html <- kable(table1, format = "html", escape = FALSE)
+writeLines(table_html, "other/tables/table1.html")
+
 
 # Table 2
 #pretest stats
@@ -43,7 +57,7 @@ p_stats <- summarize_column_stats(analysis_data, PresentationPretest)
 d_stats <- summarize_column_stats(analysis_data, DatabasesPretest)
   
 
-data <- data.frame(
+table2 <- data.frame(
   Evaluation_item = rep(c("Word Processing", "Spreadsheets", "Presentations", "Databases"), each = 5),
[…]

### 2024-04-16 paper/paper.qmd
added the data source section

@@
 ## Data Source
+
+This paper reproduces the result from @DEMARCOS2017155.
+This paper will provided a overview of the data used in that study.
+For more detailed explanation of the data please visit the original study(insert link).
 
@@
 
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
+The results from pretest(@tb-pretest) are pretty such the same for each group which aligns with the fact that this study was given before the experiment began.
 

### 2024-04-16 scripts/99-replications.R
fixed missing data in table3

@@ -77,15 +77,16 @@ w2_stats <- summarize_column_stats(analysis_data, WordProcPosttest)
 s2_stats <- summarize_column_stats(analysis_data, SpreadsheetsPosttest)
 p2_stats <- summarize_column_stats(analysis_data, PresentationPosttest)
 d2_stats <- summarize_column_stats(analysis_data, DatabasesPosttest)
+exam_stats <- summarize_column_stats(analysis_data, FinalExamination)
 
 
 table3 <- data.frame(
-  Evaluation_item = rep(c("Word Processing", "Spreadsheets", "Presentations", "Databases"), each = 5),
-  Group = rep(c("Control", "Ed. Game", "Gamification", "Social", "Social Gamif."), 4),
-  N = rep(value_counts, 4),
-  Mean = c(w2_stats$mean, s2_stats$mean, p2_stats$mean, d2_stats$mean),
-  Std_err = c(w2_stats$se, s2_stats$se, p2_stats$se, d2_stats$se),
-  Std_dev = c(w2_stats$sd, s2_stats$sd, p2_stats$sd, d2_stats$sd)
+  Evaluation_item = rep(c("Word Processing", "Spreadsheets", "Presentations", "Databases", "Final Examination"), each = 5),
+  Group = rep(c("Control", "Ed. Game", "Gamification", "Social", "Social Gamif."), 5),
+  N = rep(value_counts, 5),
+  Mean = c(w2_stats$mean, s2_stats$mean, p2_stats$mean, d2_stats$mean, exam_stats$mean),
+  Std_err = c(w2_stats$se, s2_stats$se, p2_stats$se, d2_stats$se, exam_stats$se),
+  Std_dev = c(w2_stats$sd, s2_stats$sd, p2_stats$sd, d2_stats$sd, exam_stats$sd)
 )
 
 # Saves the table to an html file

### 2024-04-16 paper/paper.qmd
wrote up data visualization section

@@
 ```
+The variables that are we are interested in seeing if share a relationship is posttest of Word Processing, Spreadsheets, Presentations, Databases and final examination.
+And we are interested in seeing the difference between the pretest(@tb-pretest) and posttest(@tb-posttest) and how each group is affect by the experiment.
 
 The results from pretest(@tb-pretest) are pretty such the same for each group which aligns with the fact that this study was given before the experiment began.
+When looking at the posttest results, the control group is lagging behind the other groups, especially in word processing, spreadsheets and databases.
+
+In word processing posttest, the group that perform the best were the social network and social gamifcation and roughly having the same performance.
+And then followed by educational game and gamification plugin.
+So it seems for word processing that groups with social elements are performing better than the group with game elements.
+
+In spreadsheets posttest, the group that perform the best was the social gamification, while the other three groups perform about the same and was only little bit behind social gamification.
+
+In presentations posttest, the group that perform the best was the educational game and not far behind was social network and gamification plugin.
+Surprisingly, social gamification was behind those three groups, as it would seem that the combination of social and game elements would make better than social network and gamification plugin.
+
+In database posttest, the educational game performed as worse the control group.
+And similarly to the presentation posttest the social gamification does worse than the social network and gamification plugin.
+And gamification plugin does slightly better than social network.
 

### 2024-04-16 paper/paper.qmd
fixed and add boxplot figures to the paper

@@
 The results from pretest(@tb-pretest) are pretty such the same for each group which aligns with the fact that this study was given before the experiment began.
-When looking at the posttest results, the control group is lagging behind the other groups, especially in word processing, spreadsheets and databases.
+When looking at the post test results(@fig-boxplot), the control group is lagging behind the other groups, especially in word processing, spreadsheets and databases.
 
-In word processing posttest, the group that perform the best were the social network and social gamifcation and roughly having the same performance.
+In word processing post test(@fig-boxplot), the group that perform the best were the social network and social gamifcation and roughly having the same performance.
 And then followed by educational game and gamification plugin.
@@
 
-In spreadsheets posttest, the group that perform the best was the social gamification, while the other three groups perform about the same and was only little bit behind social gamification.
+In spreadsheets post test(@fig-boxplot), the group that perform the best was the social gamification, while the other three groups perform about the same and was only little bit behind social gamification.
 
-In presentations posttest, the group that perform the best was the educational game and not far behind was social network and gamification plugin.
+In presentations post test(@fig-boxplot), the group that perform the best was the educational game and not far behind was social network and gamification plugin.
 Surprisingly, social gamification was behind those three groups, as it would seem that the combination of social and game elements would make better than social network and gamification plugin.
 
-In database posttest, the educational game performed as worse the control group.
+In database post test(@fig-boxplot), the educational game performed as worse the control group.
 And similarly to the presentation posttest the social gamification does worse than the social network and gamification plugin.
 And gamification plugin does slightly better than social network.
+
+```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| label: fig-boxplot
+#| fig-cap: "Boxplot showing the results of the post test for control and experiment groups "
+knitr::include_graphics(file.path(here::here(),"other/figures/figure5.png"))
+
+```
 
@@
 ```
-
-Talk way more about it.
 

### 2024-04-16 scripts/99-replications.R

@@ -100,31 +100,34 @@ plot1 <- ggplot(analysis_data, aes(x = Group, y = WordProcPosttest, color = Grou
   geom_point() +
   geom_jitter(alpha = 0.3, width = 0.15, height = 0) +
   labs(x = "Group Type", y = "Word Processing") +
-  theme(axis.text.x = element_blank())
+  scale_x_discrete(labels = c('Control', 'Ed. game', 'Gamif.', 'Social', 'Soc. Gamif.'))
+
+
 
 plot2 <- ggplot(analysis_data, aes(x = Group, y = SpreadsheetsPosttest, color = Group)) +
   geom_boxplot() +
   geom_point() +
   geom_jitter(alpha = 0.3, width = 0.15, height = 0) +
   labs(x = "Group Type", y = "Presentations") +
-  theme(axis.text.x = element_blank())
+  scale_x_discrete(labels = c('Control', 'Ed. game', 'Gamif.', 'Social', 'Soc. Gamif.'))
 
 plot3 <- ggplot(analysis_data, aes(x = Group, y = PresentationPosttest, color = Group)) +
   geom_boxplot() +
   geom_point() +
   geom_jitter(alpha = 0.3, width = 0.15, height = 0) +
   labs(x = "Group Type", y = "Word Processing") +
-  theme(axis.text.x = element_blank())
+  scale_x_discrete(labels = c('Control', 'Ed. game', 'Gamif.', 'Social', 'Soc. Gamif.'))
+  
 
 plot4 <- ggplot(analysis_data, aes(x = Group, y = DatabasesPosttest, color = Group)) +
   geom_boxplot() +
   geom_point() +
   geom_jitter(alpha = 0.3, width = 0.15, height = 0) +
   labs(x = "Group Type", y = "Databases") +
-  theme(axis.text.x = element_blank())
+  scale_x_discrete(labels = c('Control', 'Ed. game', 'Gamif.', 'Social', 'Soc. Gamif.'))
 
 fig5 <- grid.arrange(plot1, plot2, plot3, plot4, nrow = 2, ncol = 2)
-ggsave("other/figures/figure5.png", width = 10, height = 8, fig5) 
+ggsave("other/figures/figure5.png", width = 15, height = 8, fig5) 
 
 #Figure 6
 fig6 <- ggplot(analysis_data, aes(x = Group, y = FinalExamination, color = Group)) +
[…]

### 2024-04-17 paper/paper.qmd
renamed figures to match our paper and finish the rough draft for the data section

@@
 
-This paper reproduces the result from @DEMARCOS2017155.
+This paper reproduces the result from called "On the effectiveness of game-like and social approaches in learning: Comparing educational gaming, gamification & social networking" (@DEMARCOS2017155).
 This paper will provided a overview of the data used in that study.
-For more detailed explanation of the data please visit the original study(insert link).
+For more detailed explanation of the data please visit the original study.
 
@@
 Social gamified networking website use the same engine as the previous group and having similar features to Gamification plugin(@fig-social_gamification).
-A summary of the groups features and potential benefits(@tb-summary-group).
+A summary of the groups features and potential benefits(@tbl-summary-group).
 The study highlights that the educational game is not necessarily aligned with the learning goals, while the gamification used in this study was.
@@
 #| warning: false
-#| label: tb-summary-group
+#| label: tbl-summary-group
 #| tbl-cap: "Summary of the groups used, their features and potential benefits."
@@
 #| warning: false
-#| label: tb-pretest
+#| label: tbl-pretest
 #| tbl-cap: "The results of the pretest."
@@
 #| warning: false
-#| label: tb-posttest
+#| label: tbl-posttest
 #| tbl-cap: "The results of the posttest."
@@
 The variables that are we are interested in seeing if share a relationship is posttest of Word Processing, Spreadsheets, Presentations, Databases and final examination.
-And we are interested in seeing the difference between the pretest(@tb-pretest) and posttest(@tb-posttest) and how each group is affect by the experiment.
+And we are interested in seeing the difference between the pretest(@tbl-pretest) and posttest(@tbl-posttest) and how each group is affect by the experiment.
 
-The results from pretest(@tb-pretest) are pretty such the same for each group which aligns with the fact that this study was given before the experiment began.
+The results from pretest(@tbl-pretest) are pretty such the same for each group which aligns with the fact that this study was given before the experiment began.
 When looking at the post test results(@fig-boxplot), the control group is lagging behind the other groups, especially in word processing, spreadsheets and databases.
@@
 In database post test(@fig-boxplot), the educational game performed as worse the control group.
-And similarly to the presentation posttest the social gamification does worse than the social network and gamification plugin.
+And similarly to the presentation posttest the social gamification group does worse than the social network and gamification plugin.
 And gamification plugin does slightly better than social network.
+
+For the final examination(@fig-final-examination), interestingly enough, the group with the best results was the control group.
+Followed closely, by the social network group and then Educational game group.
+So the groups that performed the worse was gamfication plugin group and social gamfication group.
 
@@
 #| fig-cap: "Boxplot showing the results of the post test for control and experiment groups "
-knitr::include_graphics(file.path(here::here(),"other/figures/figure5.png"))
+knitr::include_graphics(file.path(here::here(),"other/figures/figure4.png"))
 
@@
 ```{r}
-#| label: fig-planes
-#| fig-cap: Relationship between wing length and width
 #| echo: false
+#| eval: true
 #| warning: false
 #| message: false
-
-analysis_data <- read_parquet(here::here("data/analysis_data/analysis_data.parquet"))
+#| label: fig-final-examination
+#| fig-cap: "Boxplot showing the results of the final examination for each group that particapte in this experiment"
+knitr::include_graphics(file.path(here::here(),"other/figures/figure5.png"))
 

### 2024-04-17 scripts/99-replications.R

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Replicates the tables and figures used in original study
+# Purpose: Replicates the tables and figures used in original study: https://www.sciencedirect.com/science/article/abs/pii/S0360131515300981
 # Author: Sachin Chhikara
 # Date: 11 April 2024 
 # Contact: sachin.chhikarar@utoronto.ca
@@ -94,7 +94,7 @@ table_html <- kable(table3, format = "html", escape = FALSE)
 writeLines(table_html, "other/tables/table3.html")
 
 ### Figures ###
-#Figure 5
+#Replication of Figure 5 from the orginal study
 plot1 <- ggplot(analysis_data, aes(x = Group, y = WordProcPosttest, color = Group)) +
   geom_boxplot() +
   geom_point() +
@@ -127,9 +127,9 @@ plot4 <- ggplot(analysis_data, aes(x = Group, y = DatabasesPosttest, color = Gro
   scale_x_discrete(labels = c('Control', 'Ed. game', 'Gamif.', 'Social', 'Soc. Gamif.'))
 
 fig5 <- grid.arrange(plot1, plot2, plot3, plot4, nrow = 2, ncol = 2)
-ggsave("other/figures/figure5.png", width = 15, height = 8, fig5) 
+ggsave("other/figures/figure4.png", width = 15, height = 8, fig5) 
 
-#Figure 6
+#Replication of Figure 6 from the original study
 fig6 <- ggplot(analysis_data, aes(x = Group, y = FinalExamination, color = Group)) +
   geom_boxplot() +
   geom_point() +
@@ -137,4 +137,6 @@ fig6 <- ggplot(analysis_data, aes(x = Group, y = FinalExamination, color = Group
   labs(x = "Group Type", y = "Final Examination Grade") +
   scale_x_discrete(labels = c('Control', 'Ed. game', 'Gamif.', 'Social', 'Soc. Gamif.'))
 
-ggsave("other/figures/figure6.png", fig6)
+print(fig6)
+
+ggsave("other/figures/figure5.png", width = 7, height = 5 ,fig6)

### 2024-04-17 scripts/04-model.R
updated model script

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Models the assessment given to the student against the group they were in
+# Purpose: Model created for inference about the final examination results
 # Author: Sachin Chhikara
 # Date: 12 April 2024 
 # Contact: sachin.chhikarar@utoronto.ca
@@ -14,54 +14,19 @@ library(modelsummary)
 #### Read data ####
 analysis_data <- read_parquet(file = "data/analysis_data/analysis_data.parquet")
 
-### Model data ####
-Word_model <-
-  stan_glm( 
-    formula = WordProcPosttest ~ Group,
-    data = analysis_data,
-    family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    seed = 849
-  )
-
-modelsummary(Word_model)
-
-Spreadsheet_model <-
-  stan_glm( 
-    formula = SpreadsheetsPosttest ~ Group,
-    data = analysis_data,
-    family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    seed = 849
-  )
-
-modelsummary(Spreadsheet_model)
-
-Database_model <-
-  stan_glm( 
-    formula = DatabasesPosttest ~ Group,
-    data = analysis_data,
-    family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    seed = 849
-  )
-
-modelsummary(Database_model)
-
-
 FinalExam_model <-
   stan_glm( 
-    formula = FinalExamination ~ Group,
+    formula = FinalExamination ~ Group + Gender,
     data = analysis_data,
     family = gaussian(),
     prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
+    prior_intercept = normal(0, 2.5, autoscale = TRUE),
+    prior_aux = exponential(rate = 1, autoscale = TRUE),
     seed = 853
   )
 
-modelsummary(FinalExam_model)
-
 #### Save model ####
 saveRDS(
-  first_model,
+  FinalExam_model,
   file = "models/first_model.rds"
 )

### 2024-04-17 paper/paper.qmd
model set up section is done

@@
 
-The goal of our modelling strategy is twofold. Firstly,...
-
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
+Here we briefly describe the Bayesian analysis model used to investigate final examination marks and how it is influence by the group chosen for the student and the gender of the student.
+Background details and diagnostics are included in [Appendix -@sec-model-details].
 
@@
 
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
+Define $y_i$ as the the final examination mark, which is a number 0 and 100.
+$beta_0$ is the intercept and it is the expected value of the control group.
+$group_i$ is defined as the experiment groups: educational game, gamification plugin, social network and social gamification.
+$gender_i$ is defined is binary value that is either male or female.
 
@@
 y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
+\mu_i &= \beta_0 + \beta_1 \times \mbox{group}_i + \beta_2 \times \mbox{Gender}_i\\
+\beta_0 &\sim \mbox{Normal}(0, 2.5) \\
+\beta_1 &\sim \mbox{Normal}(0, 2.5) \\
+\beta_2 &\sim \mbox{Normal}(0, 2.5) \\
 \sigma &\sim \mbox{Exponential}(1)
@@
 first_model <-
-  readRDS(file = here::here("models/first_model.rds"))
+  readRDS(file = here::here("models/final_exam.rds"))
 ```

### 2024-04-17 scripts/04-model.R

@@ -28,5 +28,5 @@ FinalExam_model <-
 #### Save model ####
 saveRDS(
   FinalExam_model,
-  file = "models/first_model.rds"
+  file = "models/final_exam.rds"
 )

### 2024-04-17 scripts/04-model.R
change the relationship bewteen the variables

@@ -16,7 +16,7 @@ analysis_data <- read_parquet(file = "data/analysis_data/analysis_data.parquet")
 
 FinalExam_model <-
   stan_glm( 
-    formula = FinalExamination ~ Group + Gender,
+    formula = FinalExamination ~ Group * Gender,
     data = analysis_data,
     family = gaussian(),
     prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
@@ -24,6 +24,8 @@ FinalExam_model <-
     prior_aux = exponential(rate = 1, autoscale = TRUE),
     seed = 853
   )
+
+modelsummary(FinalExam_model)
 
 #### Save model ####
 saveRDS(

### 2024-04-17 paper/paper.qmd
finished model section

@@
 y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \beta_0 + \beta_1 \times \mbox{group}_i + \beta_2 \times \mbox{Gender}_i\\
+\mu_i &= \beta_0 + \beta_1 \times \mbox{Group}_i \times \mbox{Gender}_i\\
 \beta_0 &\sim \mbox{Normal}(0, 2.5) \\
 \beta_1 &\sim \mbox{Normal}(0, 2.5) \\
-\beta_2 &\sim \mbox{Normal}(0, 2.5) \\
 \sigma &\sim \mbox{Exponential}(1)
@@
 
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
-
-We can use maths by including latex between dollar signs, for instance $\theta$.
+We used normal distribution for this model since our sample size was big enough(over 300 sample points), this allows to use the central limit theorem.
+We pick variable Group because we want to see how each experiment group hold up against our control group and we want to see if the game elements and social elements improve academic performance.
+We pick the gender variable since we want to see if there is a learning method that is more preferred by one gender over the other.
 

### 2024-04-17 paper/paper.qmd
explain the table model results

@@
 # Results
-
 Our results are summarized in @tbl-modelresults.
+Social gamification group grades are almost comparable to the control group as on average they tend to be lower by 1-2%.
+While, a student in the educational game group, their grades on average are 6-7% lower than the control group.
+And then, a student in social network group, their grades on average 11-12% lower than the control group.
+Lastly, a student in the gamification plugin group, their grades on average are 15-16% lower than the control group.
 
@@
 
-first_model <-
+finalExam_model <-
   readRDS(file = here::here("models/final_exam.rds"))
@@
 #| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
+#| tbl-cap: "Explanatory models of Final Exam marks based off of the experiment group and gender"
 #| warning: false
@@
   list(
-    "First model" = first_model
+    "Final Exam Marks" = finalExam_model
   ),
@@
 
-## First discussion point
+## Design of Gamification
 
@@
 
-## Second discussion point
+## Good example of Gamification
 
-## Third discussion point
+## Student's opinon about it
 
@@
 #| fig-subcap: ["Trace plot", "Rhat plot"]
-#| layout-ncol: 2
 
-plot(first_model, "trace")
+plot(finalExam_model, "trace")
 
-plot(first_model, "rhat")
+plot(finalExam_model, "rhat")
 ```

### 2024-04-17 scripts/04-model.R

@@ -25,8 +25,6 @@ FinalExam_model <-
     seed = 853
   )
 
-modelsummary(FinalExam_model)
-
 #### Save model ####
 saveRDS(
   FinalExam_model,

### 2024-04-17 paper/paper.qmd
fixed table1 and finish the data section

@@
 The original study used 379 undergraduates for their experiments and there were randomly assigned into 5 groups Control(N=76), Educational game(N=75), Gamification Plugin(N=77), Social networking website(N=75), Social gamified networking website(N=76).
-The experiment was carried out on 10-week first year undergraduate class called ‘Qualification for ICT Users’ with hybrid learning.
+The experiment was carried out on 10-week first year undergraduate class called ‘Qualification for ICT Users’ with blended learning.
 This course is an introduction to basic computing concepts such as word processing, spreadsheets, presentations and databases.
-There is an assignment for each of these four concepts which focus on testing practical skills.
-While, the final examination is cumulative and focus on testing conceptual knowledge.
 
-Students have lecture every two weeks and must work independently rest of the work to learn then material.
-Supplementary learning material was provided such as videos and communication tools in learning material platform.
+In this experiment, before applying the corresponding learning methods, the students take a pretest, which occurs in week 1.
+And through week 2-9, depending on the group the student was assigned they learn using that specific method.
+During those weeks, they were assigned four assignments(aka post tests) on week 3, 5, 7 and 9.
+In addition, these assignments are on word processing, spreadsheets, presentations and databases, which tests students on practical skills.
+Finally, there is cumulative final exam and tests students on conceptual knowledge.
 
-The control group just use what was mention above.
+All groups had students have lecture every two weeks and must work independently rest of the work to learn then material using their respective method.
+In addition, Supplementary learning material was provided such as videos and communication tools in learning material platform.
+The control group just use traditional e-learning approach that was mention above.
 Educational game used was called Ribbonhero offered by Microsoft as as free download to download Software, and player plays as virtual character Clippy and must overcome six challenges with increasing difficulty.
@@
 
-htmltools::includeHTML(file.path(here::here(),"other/tables/table1.html"))
+knitr::include_graphics(file.path(here::here(),"other/tables/table1.jpg"))
 ```
 
-## Data Cleaning Procedure
+## Variables of Interest and Data Cleaning Procedure
+The variables used in this study are Group, Gender, pretest and post test for Word Processing, Spreadsheets, Presentation, Databases and FinalExamination.
+Pretest, post test and FinalExamination use the measurement of a grade, which is from 0 - 100%.
 
@@
 
-## Design of Gamification
+## Is Gamification effective? Does it have pontential to change the educational system?
 
@@
 
-## Good example of Gamification
+## Design of Gamification
 
-## Student's opinon about it
+## Student's input
 

### 2024-04-17 scripts/99-replications.R

@@ -34,20 +34,6 @@ summarize_column_stats <- function(data, column_name) {
 
 
 #### Tables ####
-# Table 1
-
-# Note: This table was used in original study, but the table code was not provided.
-# So replicate it, we took a screenshot of the table and told chatgpt to create this table.
-table1 <- data.frame(
-  Instrument = c("Educational game", "Gamification plugin", "Social networking website", "Social gamification website"),
-  Features = c("Challenges, levels, points, narrative", "Trophies, badges, challenges, leaderboard", "Blogging, questions & answers, liking, friends, built-in twitter, dashboard", "Blogging, questions & answers, liking, friends, built-in twitter, dashboard, challenges, points, achievements, virtual currency, shop, external rewarding, personalization (status/visibility), peer review"),
-  `Approach & targeted benefits` = c("Not aligned with learning objectives Independent work & exploration of students", "Competition-driven Motivate participation through comparison with peers", "Cooperation and communication among participants. Boost participation, collaborative work & community building Promote student-driven discussion", "Competition and cooperation Boost participation, collaborative work & community building Motivate participation through comparison with peers Social interaction affords additional means to motivate participation and engagement Addressing needs of different students (player types) and widen participation")
-)
-
-# Saves the table to an html file
-table_html <- kable(table1, format = "html", escape = FALSE)
-writeLines(table_html, "other/tables/table1.html")
-
 
 # Table 2
 #pretest stats
@@ -136,7 +122,5 @@ fig6 <- ggplot(analysis_data, aes(x = Group, y = FinalExamination, color = Group
   geom_jitter(alpha = 0.3, width = 0.15, height = 0) +
   labs(x = "Group Type", y = "Final Examination Grade") +
   scale_x_discrete(labels = c('Control', 'Ed. game', 'Gamif.', 'Social', 'Soc. Gamif.'))
-
-print(fig6)
 
 ggsave("other/figures/figure5.png", width = 7, height = 5 ,fig6)

### 2024-04-18 paper/paper.qmd
result section is done

@@
 
-## Data Visualization
-
-```{r}
-#| eval: true
-#| echo: false
-#| message: false
-#| warning: false
-#| label: tbl-pretest
-#| tbl-cap: "The results of the pretest."
-
-htmltools::includeHTML(file.path(here::here(),"other/tables/table2.html"))
-```
-
-```{r}
-#| eval: true
-#| echo: false
-#| message: false
-#| warning: false
-#| label: tbl-posttest
-#| tbl-cap: "The results of the posttest."
-
-htmltools::includeHTML(file.path(here::here(),"other/tables/table3.html"))
-```
-The variables that are we are interested in seeing if share a relationship is posttest of Word Processing, Spreadsheets, Presentations, Databases and final examination.
-And we are interested in seeing the difference between the pretest(@tbl-pretest) and posttest(@tbl-posttest) and how each group is affect by the experiment.
-
-The results from pretest(@tbl-pretest) are pretty such the same for each group which aligns with the fact that this study was given before the experiment began.
-When looking at the post test results(@fig-boxplot), the control group is lagging behind the other groups, especially in word processing, spreadsheets and databases.
-
-In word processing post test(@fig-boxplot), the group that perform the best were the social network and social gamifcation and roughly having the same performance.
-And then followed by educational game and gamification plugin.
-So it seems for word processing that groups with social elements are performing better than the group with game elements.
-
-In spreadsheets post test(@fig-boxplot), the group that perform the best was the social gamification, while the other three groups perform about the same and was only little bit behind social gamification.
-
-In presentations post test(@fig-boxplot), the group that perform the best was the educational game and not far behind was social network and gamification plugin.
-Surprisingly, social gamification was behind those three groups, as it would seem that the combination of social and game elements would make better than social network and gamification plugin.
-
-In database post test(@fig-boxplot), the educational game performed as worse the control group.
-And similarly to the presentation posttest the social gamification group does worse than the social network and gamification plugin.
-And gamification plugin does slightly better than social network.
-
-For the final examination(@fig-final-examination), interestingly enough, the group with the best results was the control group.
-Followed closely, by the social network group and then Educational game group.
-So the groups that performed the worse was gamfication plugin group and social gamfication group.
-
-```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-#| label: fig-boxplot
-#| fig-cap: "Boxplot showing the results of the post test for control and experiment groups "
-knitr::include_graphics(file.path(here::here(),"other/figures/figure4.png"))
-
-```
-
-```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-#| label: fig-final-examination
-#| fig-cap: "Boxplot showing the results of the final examination for each group that particapte in this experiment"
-knitr::include_graphics(file.path(here::here(),"other/figures/figure5.png"))
-
-```
-
 # Model
@@
 # Results
-Our results are summarized in @tbl-modelresults.
+
+```{r}
+#| eval: true
+#| echo: false
+#| message: false
+#| warning: false
+#| label: tbl-pretest
+#| tbl-cap: "The results of the pretest."
+
+htmltools::includeHTML(file.path(here::here(),"other/tables/table2.html"))
+```
+
+```{r}
+#| eval: true
+#| echo: false
+#| message: false
+#| warning: false
+#| label: tbl-posttest
+#| tbl-cap: "The results of the posttest."
+
+htmltools::includeHTML(file.path(here::here(),"other/tables/table3.html"))
+```
+
+The results from pretest(@tbl-pretest) are pretty such the same for each group which aligns with the fact that this study was given before the experiment began.
+When looking at the post test results(@fig-boxplot), the control group is lagging behind the other groups, especially in word processing, spreadsheets and databases.
+
+In word processing post test(@fig-boxplot), the group that perform the best were the social network and social gamifcation and roughly having the same performance.
+And then followed by educational game and gamification plugin.
+So it seems for word processing that groups with social elements are performing better than the group with game elements.
+
+In spreadsheets post test(@fig-boxplot), the group that perform the best was the social gamification, while the other three groups perform about the same and was only little bit behind social gamification.
+
+In presentations post test(@fig-boxplot), the group that perform the best was the educational game and not far behind was social network and gamification plugin.
+Surprisingly, social gamification was behind those three groups, as it would seem that the combination of social and game elements would make better than social network and gamification plugin.
+
+In database post test(@fig-boxplot), the educational game performed as worse the control group.
+And similarly to the presentation posttest the social gamification group does worse than the social network and gamification plugin.
+And gamification plugin does slightly better than social network.
+
+For the final examination(@fig-final-examination), interestingly enough, the group with the best results was the control group.
+Followed closely, by the social network group and then Educational game group.
+So the groups that performed the worse was gamfication plugin group and social gamfication group.
+
+Our model results are summarized in @tbl-modelresults.
 Social gamification group grades are almost comparable to the control group as on average they tend to be lower by 1-2%.
@@
 Lastly, a student in the gamification plugin group, their grades on average are 15-16% lower than the control group.
+
+```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| label: fig-boxplot
+#| fig-cap: "Boxplot showing the results of the post test for control and experiment groups "
+knitr::include_graphics(file.path(here::here(),"other/figures/figure4.png"))
+
+```
+
+```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| label: fig-final-examination
+#| fig-cap: "Boxplot showing the results of the final examination for each group that particapte in this experiment"
+knitr::include_graphics(file.path(here::here(),"other/figures/figure5.png"))
+
+```
 

### 2024-04-18 paper/paper.qmd
first paragraph for the first dicussion point

@@
 
-## Is Gamification effective? Does it have pontential to change the educational system?
+## Is Gamification effective? And is it better for male or females?
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+First, let us take a look at post test(@tbl-posttest) table again, recall that social gamification and social network does the best at word processing.
+Furthermore, social gamification does the best at spreadsheets as well.
+In addition, educational game does the best in presentations and gamification plugin does the best in databases.
+Notice that for post test, the best groups in each assessment seems to be related to groups that have game elements.
+Another thing to highlight is that social network group when comes to post tests tend to always be in top three groups.
+And social gamifcation is the best in 2/4 post tests.
+So it so seems that groups with social elements also perform well.
 

### 2024-04-18 paper/paper.qmd
added info about gender in results
added replication link

@@
   - Sachin Chhikara
-thanks: "Code and data are available at: LINK."
+thanks: "Code and data are available at: https://github.com/SachinChhikara/Effectiveness_of_Gamification_Education."
 date: today
@@
 
+Males overall on average did better than females by 2-3%.
+Also, males in the gamification plugin group on average did better that females by 1-2%.
+Interestingly, males do 2-4% worse than females in educational game, social gamification and social network group.
+
 ```{r}

### 2024-04-18 paper/paper.qmd
use lintr and styler

@@
 
-finalExam_model <-
+final_exam_model <-
   readRDS(file = here::here("models/final_exam.rds"))
@@
   list(
-    "Final Exam Marks" = finalExam_model
+    "Final Exam Marks" = final_exam_model
   ),
@@
 
-plot(finalExam_model, "trace")
+plot(final_exam_model, "trace")
 
-plot(finalExam_model, "rhat")
+plot(final_exam_model, "rhat")
 ```

### 2024-04-18 scripts/00-simulate_data.R

@@ -1,7 +1,7 @@
 #### Preamble ####
 # Purpose: Simulates Postive effects of Gamification
 # Author: Sachin Chhikara
-# Date: 26 March 2024 
+# Date: 26 March 2024
 # Contact: sachin.chhikarar@utoronto.ca
 # License: MIT
 
@@ -46,12 +46,9 @@ data %>%
   gather(key = "Variable", value = "Value", -Gender) %>%
   ggplot(aes(x = Value, fill = Gender)) +
   geom_histogram(binwidth = 5, position = "dodge", alpha = 0.7) +
-  facet_wrap(~ Variable, scales = "free") +
-  labs(title = "Comparison of Male and Female",
-       x = "Value", y = "Frequency") +
+  facet_wrap(~Variable, scales = "free") +
+  labs(
+    title = "Comparison of Male and Female",
+    x = "Value", y = "Frequency"
+  ) +
   theme_minimal()
-
-
-
-
-

### 2024-04-18 scripts/02-data_cleaning.R

@@ -1,7 +1,7 @@
 #### Preamble ####
 # Purpose: Cleans the raw data
 # Author: Sachin Chhikara
-# Date: 8 April 2024 
+# Date: 8 April 2024
 # Contact: sachin.chhikarar@utoronto.ca
 # License: MIT
 
@@ -16,18 +16,17 @@ raw_data <- read_csv("data/raw_data/1-s2.0-S2352340917300173-mmc2.csv")
 cleaned_data <-
   raw_data |>
   select(-Age) |>
-  mutate(Group = case_when(
-    Group == 0 ~ "Control group",
-    Group == 1 ~ "Educational game",
-    Group == 2 ~ "Gamification plugin",
-    Group == 3 ~ "Social networking website",
-    Group == 4 ~ "Social gamified networking website"
-  ),
-  Gender = case_when(Gender == "M" ~ "Male", Gender == "F" ~ "Female")
+  mutate(
+    Group = case_when(
+      Group == 0 ~ "Control group",
+      Group == 1 ~ "Educational game",
+      Group == 2 ~ "Gamification plugin",
+      Group == 3 ~ "Social networking website",
+      Group == 4 ~ "Social gamified networking website"
+    ),
+    Gender = case_when(Gender == "M" ~ "Male", Gender == "F" ~ "Female")
   ) |>
   tidyr::drop_na()
-  
-
 
 
 #### Save data ####

### 2024-04-18 scripts/03-test_data.R

@@ -1,7 +1,7 @@
 #### Preamble ####
 # Purpose: Run tests on the analysis data
 # Author: Sachin Chhikara
-# Date: 8 April 2024 
+# Date: 8 April 2024
 # Contact: sachin.chhikarar@utoronto.ca
 # License: MIT
 
@@ -12,7 +12,7 @@ library(arrow)
 
 analysis_data <- read_parquet("data/analysis_data/analysis_data.parquet")
 
-##Helper functions
+## Helper functions
 is_column_of_type <- function(dataframe, column_name, datatype) {
   column_class <- class(dataframe[[column_name]])
   return(datatype %in% column_class)
@@ -42,62 +42,77 @@ check_values_between_0_and_100 <- function(column_values_list) {
     column_values <- column_values_list[[i]][[1]]
     column_name <- column_values_list[[i]][[2]]
     if (all(column_values >= 0 & column_values <= 100)) {
-      message(paste(column_name, ": The values are between 0 and 100 as expected"))
+      message(paste(column_name, ":
+                    The values are between 0 and 100 as expected"))
     } else {
-      message(paste(column_name, "Error: There is an inappropriate value in this dataset. Double check that the dataset was modified incorrectly or remove that value from the dataset if necessary"))
+      message(paste(
+        column_name,
+        "Error: There is an inappropriate value in this dataset.
+                    Double check that the dataset was modified incorrectly or
+                    remove that value from the dataset if necessary"
+      ))
     }
   }
 }
 
 #### Test data ####
-#1.Proper datatype is used for each column 
+# 1.Proper datatype is used for each column
 if (is_column_of_type(analysis_data, "Group", "character")) {
-  "The numeric values in this column had their numeric values converted to their character represntation"
-}else{
-  "The numeric values have not been converted, please makes sure to run the 02_data_cleaning.R"
+  "The numeric values in this column had their numeric values
+  converted to their character represntation"
+} else {
+  "The numeric values have not been converted, please makes sure to
+  run the 02_data_cleaning.R"
 }
 
 
 check_gender_values(analysis_data, "gender", c("male", "female"))
 
-check_numeric_columns(analysis_data, c("WordProcPretest", "SpreadsheetsPretest", 
-                                       "PresentationPretest", "DatabasesPretest"))
[…]

### 2024-04-18 scripts/04-model.R

@@ -1,7 +1,7 @@
 #### Preamble ####
 # Purpose: Model created for inference about the final examination results
 # Author: Sachin Chhikara
-# Date: 12 April 2024 
+# Date: 12 April 2024
 # Contact: sachin.chhikarar@utoronto.ca
 # License: MIT
 
@@ -14,8 +14,8 @@ library(modelsummary)
 #### Read data ####
 analysis_data <- read_parquet(file = "data/analysis_data/analysis_data.parquet")
 
-FinalExam_model <-
-  stan_glm( 
+final_exam_model <-
+  stan_glm(
     formula = FinalExamination ~ Group * Gender,
     data = analysis_data,
     family = gaussian(),
@@ -27,6 +27,6 @@ FinalExam_model <-
 
 #### Save model ####
 saveRDS(
-  FinalExam_model,
+  final_exam_model,
   file = "models/final_exam.rds"
 )

### 2024-04-18 scripts/99-replications.R

@@ -1,7 +1,8 @@
 #### Preamble ####
-# Purpose: Replicates the tables and figures used in original study: https://www.sciencedirect.com/science/article/abs/pii/S0360131515300981
+# Purpose: Replicates the tables and figures used in original study:
+# https://www.sciencedirect.com/science/article/abs/pii/S0360131515300981
 # Author: Sachin Chhikara
-# Date: 11 April 2024 
+# Date: 11 April 2024
 # Contact: sachin.chhikarar@utoronto.ca
 # License: MIT
 
@@ -15,7 +16,7 @@ library(gridExtra)
 #### Load data ####
 analysis_data <- read_parquet(file = "data/analysis_data/analysis_data.parquet")
 
-#number of people in each group
+# number of people in each group
 value_counts <- table(analysis_data$Group)
 
 
@@ -24,11 +25,11 @@ summarize_column_stats <- function(data, column_name) {
   stats <- data %>%
     group_by(Group) %>%
     summarise(
-      mean = round(mean({{column_name}}), 2),
-      sd = round(sd({{column_name}}), 2),
-      se = round(sd({{column_name}})/sqrt(n()), 2)
+      mean = round(mean({{ column_name }}), 2),
+      sd = round(sd({{ column_name }}), 2),
+      se = round(sd({{ column_name }}) / sqrt(n()), 2)
     )
-  
+
   return(stats)
 }
 
@@ -36,16 +37,22 @@ summarize_column_stats <- function(data, column_name) {
 #### Tables ####
 
 # Table 2
-#pretest stats
+# pretest stats
 w_stats <- summarize_column_stats(analysis_data, WordProcPretest)
 s_stats <- summarize_column_stats(analysis_data, SpreadsheetsPretest)
 p_stats <- summarize_column_stats(analysis_data, PresentationPretest)
 d_stats <- summarize_column_stats(analysis_data, DatabasesPretest)
-  
+
 
 table2 <- data.frame(
-  Evaluation_item = rep(c("Word Processing", "Spreadsheets", "Presentations", "Databases"), each = 5),
-  Group = rep(c("Control", "Ed. Game", "Gamification", "Social", "Social Gamif."), 4),
+  Evaluation_item = rep(c(
[…]

### 2024-04-18 paper/paper.qmd
finish first dicussion point

@@
 
+Gamification is not effective as we anticipated as seen in the final exam marks where the control group did the best.
+But, when comes to post tests as we note earlier groups with game elements were doing the best.
+And even for final examination social gamification was doing almost as good as the control group.
+From this study, we can conclude that gamification may not be good as we hope but it has potential to be better than traditional education.
+While, from our study we found males perform slightly better than females, the difference is pretty small(2-4%), which is good since both males and females can benefit equally from gamification.
+Furthermore, in order to improve gamification we will need to look at two things the design and student's feedback.
+
 ## Design of Gamification
 
-## Student's input
+## Student's feedback
 

### 2024-04-18 paper/paper.qmd
rough draft for second dicussion point

@@
 
+Like I mentioned before gamification has to potential to change the traditional educational system, but in order to do that need to design it in a way that truly benefits the students.
+A leading expert in gamification and behavioral drive, Yu-kai Chou, has a create framework for gamification called the Octalysis Framework(reference to the figure in the appendix).Looking at the framework there are eight main points mention: Epic Meaning, Accomplishment, Empowerment, Ownership, Social Influence, Scarcity, Unpredictability, and Avoidance.
+
+Let us see how this framework applies to our study, for this example we will using social gamification group, since it one of the better performing groups with game elements.
+Epic Meaning category it is might but some students as they believe if they do well in this course, it could lead to some future goal like their dream job.
+Accomplishment is achieved by the meaningful challenges provided in each module and achievements.
+Empowerment is achieved by peer reviews and feedback from the teacher as well.
+Ownership is achieved as they can customize their profiles and status.
+Social Influence is achieved by being able to add friends and being able to features similar to Twitter(known as X now).
+This study has 5 out of 8 main points mention from the framework.
+
+Another example that we want to apply this framework is on a popular gamification language learning app, called Duolingo.
+
 ## Student's feedback

### 2024-04-18 paper/paper.qmd
finished the second dicussion point

@@
 A leading expert in gamification and behavioral drive, Yu-kai Chou, has a create framework for gamification called the Octalysis Framework(reference to the figure in the appendix).Looking at the framework there are eight main points mention: Epic Meaning, Accomplishment, Empowerment, Ownership, Social Influence, Scarcity, Unpredictability, and Avoidance.
+For even more in depth explanation, please visit Yu-kai website:https://yukaichou.com/gamification-examples/octalysis-complete-gamification-framework/.
 
@@
 Another example that we want to apply this framework is on a popular gamification language learning app, called Duolingo.
-
+Duolingo is a free app that has miliions of user ranging from public students in third world countries to even hollywood stars.
+Yu-kai Chou website provides an analysis for Duolingo, which has 6 out of 8 elements of the framework and here I am going to highlight some of the elements.
+Firstly, Epic Meaning is to learn a language and the app even asks the user when creating an account what is their purpose for learning new language.
+Secondly, Ownership, users have a currency call Lingots which allows players to buy Power-Ups(ways to make the player stronger) such as streak freeze and to buy clothes for their player character.
+Lastly, it has Scarcity and Avoidance as player have a limited amount of lives and if they lose then they can no longer play for a certain of time.
 ## Student's feedback

### 2024-04-18 paper/paper.qmd
Finish limatations and weakness section

@@
 # Data
-
 ## Data Source
-
 This paper reproduces the result from called "On the effectiveness of game-like and social approaches in learning: Comparing educational gaming, gamification & social networking" (@DEMARCOS2017155).
@@
 ## Methodology
-
 The original study used 379 undergraduates for their experiments and there were randomly assigned into 5 groups Control(N=76), Educational game(N=75), Gamification Plugin(N=77), Social networking website(N=75), Social gamified networking website(N=76).
@@
 ## Variables of Interest and Data Cleaning Procedure
+
 The variables used in this study are Group, Gender, pretest and post test for Word Processing, Spreadsheets, Presentation, Databases and FinalExamination.
@@
 # Results
-
 ```{r}
@@
 Lastly, it has Scarcity and Avoidance as player have a limited amount of lives and if they lose then they can no longer play for a certain of time.
-## Student's feedback
 
-## Weaknesses and next steps
+## Limations and Weaknessess
+Limitations of this dataset is that doesn't tell us how student's satisfaction, retention, motivation and engagement.
+This is would useful information since it will paint us better picture on the effectiveness of gamification.
+In addition, if students don't really like then it would be indicator whether gamification is not working or that something missing that could improve it.
+According to (@article), some aspects of academic boredom comes from lack of motivation and learning methods, so if gamification can solve this would a huge win for students and for society at a whole.
+Furthermore, if students really enjoy gamification then this means this a potential valid leanring method, which could convince others to fund and study further.
+
+Weakness of this dataset is that age column take the average age, which is 19 years in this case and gives every student that age.
+If the dataset gave us every student's age or even age range this could useful in determining which age group was benefiting more from gamification.
+It could that told us younger students better with gamification, but old students preform better with the traditional learning system.
+
+## Future Studies
 

### 2024-04-19 paper/paper.qmd
finish the dicussion section

@@
 #| eval: true
+#| label: tbl-modelresults
+#| tbl-cap: "Explanatory models of Final Exam marks based off of the experiment group and gender"
 #| warning: false
-#| message: false
-
 library(rstanarm)
@@
   readRDS(file = here::here("models/final_exam.rds"))
-```
-
-```{r}
-#| echo: false
-#| eval: true
-#| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of Final Exam marks based off of the experiment group and gender"
-#| warning: false
 
@@
 Like I mentioned before gamification has to potential to change the traditional educational system, but in order to do that need to design it in a way that truly benefits the students.
-A leading expert in gamification and behavioral drive, Yu-kai Chou, has a create framework for gamification called the Octalysis Framework(reference to the figure in the appendix).Looking at the framework there are eight main points mention: Epic Meaning, Accomplishment, Empowerment, Ownership, Social Influence, Scarcity, Unpredictability, and Avoidance.
+A leading expert in gamification and behavioral drive, Yu-kai Chou, has a create framework for gamification called the Octalysis Framework(reference to the figure in the appendix).Looking at the framework there are eight core drives: Epic Meaning, Accomplishment, Empowerment, Ownership, Social Influence, Scarcity, Unpredictability, and Avoidance.
 For even more in depth explanation, please visit Yu-kai website:https://yukaichou.com/gamification-examples/octalysis-complete-gamification-framework/.
@@
 Social Influence is achieved by being able to add friends and being able to features similar to Twitter(known as X now).
-This study has 5 out of 8 main points mention from the framework.
+This study has 5 out of 8 core drives mention from the framework.
 
 Another example that we want to apply this framework is on a popular gamification language learning app, called Duolingo.
-Duolingo is a free app that has miliions of user ranging from public students in third world countries to even hollywood stars.
+Duolingo is a free app that has millions of user ranging from public students in third world countries to even Hollywood stars.
 Yu-kai Chou website provides an analysis for Duolingo, which has 6 out of 8 elements of the framework and here I am going to highlight some of the elements.
@@
 In addition, if students don't really like then it would be indicator whether gamification is not working or that something missing that could improve it.
-According to (@article), some aspects of academic boredom comes from lack of motivation and learning methods, so if gamification can solve this would a huge win for students and for society at a whole.
-Furthermore, if students really enjoy gamification then this means this a potential valid leanring method, which could convince others to fund and study further.
+According to study about academic boredom (@article), some aspects of it comes from lack of motivation and learning methods, so if gamification can solve this would a huge win for students and for society at a whole.
+Furthermore, if students really enjoy gamification then this means this a potential valid learning method, which could convince others to fund and study further.
 
@@
 
-Weaknesses and next steps should also be included.
-
+Like I mentioned before, this paper shows that gamification has potential to surpass traditional educational system.
+In future studies, more attention should be put into designing the gamification aspect.
+The Octalysis framework should be used and the design should it is best to meet all 8 core drives.
+Furthermore, Yu-kai is open to collaboration and consulting so that could make the design even more robust as there is more than just this framework that he talks on his website.
+In addition, there should focus on social elements as well since that experiement did well in post tests.
+Lastly, this design is probably going to need multiple iterations and constant feedback from the students to further improve it and to allow it eventually surpass the traditional education system.
 \newpage

### 2024-04-19 paper/paper.qmd
finsihed the appendix

@@
 Here we briefly describe the Bayesian analysis model used to investigate final examination marks and how it is influence by the group chosen for the student and the gender of the student.
-Background details and diagnostics are included in [Appendix -@sec-model-details].
+Background details are included in [Appendix @fig-ppcheckandposteriorvsprior].
 
@@
 ```
+\newpage
 
@@
 Like I mentioned before gamification has to potential to change the traditional educational system, but in order to do that need to design it in a way that truly benefits the students.
-A leading expert in gamification and behavioral drive, Yu-kai Chou, has a create framework for gamification called the Octalysis Framework(reference to the figure in the appendix).Looking at the framework there are eight core drives: Epic Meaning, Accomplishment, Empowerment, Ownership, Social Influence, Scarcity, Unpredictability, and Avoidance.
+A leading expert in gamification and behavioral drive, Yu-kai Chou, has a create framework for gamification called the Octalysis Framework(@fig-framework).Looking at the framework there are eight core drives: Epic Meaning, Accomplishment, Empowerment, Ownership, Social Influence, Scarcity, Unpredictability, and Avoidance.
 For even more in depth explanation, please visit Yu-kai website:https://yukaichou.com/gamification-examples/octalysis-complete-gamification-framework/.
@@
 Lastly, it has Scarcity and Avoidance as player have a limited amount of lives and if they lose then they can no longer play for a certain of time.
+
+```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| label: fig-framework
+#| fig-cap: "The Octalysis Framework for Gamification & Behavioral Design"
+knitr::include_graphics(file.path(here::here(),"other/figures/octalysis_framework.jpg"))
+
+```
 
@@
 
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
+In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check.
 
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
+In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior.
+
+These two graphs to do a good job of showing that the data is properly fitted.
 
@@
 
+analysis_data <- read_parquet(file.path(here::here(),"data/analysis_data/analysis_data.parquet"))
+
+pp_check(final_exam_model) +
+  theme_classic() +
+  theme(legend.position = "bottom")
+
+posterior_vs_prior(final_exam_model) +
+  theme_minimal() +
+  scale_color_brewer(palette = "Set1") +
+  theme(legend.position = "bottom") +
+  coord_flip()
+
 ```
 
-## Diagnostics
-
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
-
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
-
-```{r}
-#| echo: false
-#| eval: true
-#| message: false
-#| warning: false
-#| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
-
-plot(final_exam_model, "trace")
-
-plot(final_exam_model, "rhat")
 ```

### 2024-04-19 paper/paper.qmd
Added a title and abstract

@@
 ---
-title: "Gamification Effectiveness on Education"
+title: "Gamification can Change the Traditonal Educational System"
 author: 
@@
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "In this paper a reproduction of 'On the effectiveness of game-like and social approaches in learning: Comparing educational gaming, gamification & social networking' was done.
+We discoved that gamification while not as effective as intial thought, it has the pontential to be better than traditonal educational system especially when comes to assignments.
+These results are important as it suggested that students can perform even better academically."
 format: pdf
@@
 The Octalysis framework should be used and the design should it is best to meet all 8 core drives.
-Furthermore, Yu-kai is open to collaboration and consulting so that could make the design even more robust as there is more than just this framework that he talks on his website.
+Furthermore, Yu-kai is open to collaboration and consulting so that could make the design even better as there is more than just this framework that he talks about on his website.
 In addition, there should focus on social elements as well since that experiement did well in post tests.

### 2024-04-19 paper/datasheet_template.qmd
started working on datasheet

---
title: "Datasheet for 'On the effectiveness of game-like and social approaches in learning: Comparing educational gaming, gamification & social networking'"
author: 
  - Sachin Chhikara
thanks: "Code and data are available at: https://github.com/SachinChhikara/Effectiveness_of_Gamification_Education."
date: today
date-format: long
format: pdf
number-sections: true
bibliography: references.bib
---

Extract of the questions from @gebru2021datasheets.

**Motivation**

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The dataset was created to enable analysis of comparing game-like and social approaches 
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - TBD
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - TBD
4. *Any other comments?*
    - No

**Composition**

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*
	- TBD
2. *How many instances are there in total (of each type, if appropriate)?*
	- TBD
3. *Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
	- TBD
4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
	- TBD
5. *Is there a label or target associated with each instance? If so, please provide a description.*
	- TBD
6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*
	- TBD
7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
	- TBD
8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
	- TBD
9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
	- TBD
10. *Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
	- TBD
11. *Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)? If so, please provide a description.*
	- TBD
12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
	- TBD
13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
	- TBD
14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*
	- TBD
15. *Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)? If so, please provide a description.*
	- TBD
16. *Any other comments?*
	- TBD

**Collection process**

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- TBD
2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- TBD
3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	- TBD
4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	- TBD
5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	- TBD
6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- TBD
7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- TBD
8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	- TBD
9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- TBD
10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- TBD
11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- TBD
12. *Any other comments?*
	- TBD

**Preprocessing/cleaning/labeling**

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- TBD
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- TBD
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- TBD
4. *Any other comments?*
	- TBD

**Uses**

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- TBD
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- TBD
3. *What (other) tasks could the dataset be used for?*
	- TBD
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- TBD
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- TBD
6. *Any other comments?*
	- TBD

**Distribution**

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- TBD
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- TBD
3. *When will the dataset be distributed?*
	- TBD
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- TBD
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- TBD
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- TBD
7. *Any other comments?*
	- TBD

**Maintenance**

1. *Who will be supporting/hosting/maintaining the dataset?*
	- TBD
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- TBD
3. *Is there an erratum? If so, please provide a link or other access point.*
	- TBD
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- TBD
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- TBD
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- TBD
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- TBD
8. *Any other comments?*
	- TBD

\newpage

# References

### 2024-04-19 paper/paper.qmd
add another paragraph to limations and weaknees section

@@
 date-format: long
-abstract: "In this paper a reproduction of 'On the effectiveness of game-like and social approaches in learning: Comparing educational gaming, gamification & social networking' was done.
+abstract: "In this paper a reproduction of the paper 'On the effectiveness of game-like and social approaches in learning: Comparing educational gaming, gamification & social networking' was done.
 We discoved that gamification while not as effective as intial thought, it has the pontential to be better than traditonal educational system especially when comes to assignments.
@@
 Games have been part of human history for a long time and are loved by many young and old.
-The design behind why game are so fun have investigated in recent time and how to apply those element that are fun and to apply them to other fields, this is known as gamification.
-Gamification is used in fields such as enterprise, sales, lifestyle and education.
-In this paper we will focusing on application of education, we be using data from Duolingu, training model and making inference off, real life application of gamification to an individual productive.
+Games are able to keep players engage, motivate and give the feeling of accomplishment.
+Due to this, recently people have been studying games and trying to understand how to apply these concepts to non-game related fields, this is known as gamification.
+Gam
 
@@
 
+Another weakness of this study is that study it reproduce is about 10 years old.
+This mean that data may not hold up as well.
+But there are not many gamification studies that compare treatment to a experiment group, and with open source data to boot.
+Also, Duolingo is popular language learn app, which use gamification and it has millions of active users which suggest that gamification is not a dead field and it is clearly effective for learning languages.
+
 ## Future Studies

### 2024-04-19 paper/paper.qmd
finished the introduction section

@@
 Due to this, recently people have been studying games and trying to understand how to apply these concepts to non-game related fields, this is known as gamification.
-Gam
+And it is used in many fields such as enterprise, sales, lifestyle, education and etc.
 
-In this paper, we are doing replication of a study ...
-, which has a control and treatment where the treatment is applied gamification, while the control is using an ordinary education system.
-Yeah there benefits, but there are downside when comes to how the gamification as it might discourage learning.
-Furthermore, an wide use application of gamification is a language learning app called Duolingo, which has ...
-active users and this app learning is recognized in certain Universities as legitimate English learning.So we examine game design that are use.
-Ways to apply gamification in daily lives, like this app called Habitica: Gamify your tasks.
+The focus of this paper will be an application of gamification in the education field. In this paper, we are doing a reproduction of paper called
+"On the effectiveness of game-like and social approaches in learning: Comparing educational gaming, gamification & social networking".
+In this paper, they took a control group, students using a traditional educational system and four treatment groups, which were students using different learning approaches which involved social and game elements.
+The focus of the study was to see if gamifcation was effective and this was achieve by looking at academic performance of the groups.And just like original paper we will focus on effective of gamifcation, using the grades of the students, which range from 0 - 100%.
+In addition, we will also be asking the question whether gamification works better for male or female.
+
+And what we found in this paper is that gamification may not be as effective for examinations, but it works well for assignment.
+Even then there is still room for improvement in the design and this can help to enliven student's education.
+And if we are to motive students this can help their lives and others, which can create a more positive impact on society.
+
+This current section is introduction, the next section is data section where we discuss the data used and explore it.
+Then, we have a section where create a model out of such data and explain the reasoning behind our model design it.
+After that, we have results section where we talk about figures and tables that were replicate from the original paper and the model results.
+Lastly, we have the discussion section where discuss the results and how it connects to outside world.
 

### 2024-04-19 paper/paper.qmd
added the data cleaning section

@@
 Pretest, post test and FinalExamination use the measurement of a grade, which is from 0 - 100%.
+
+The R package used for cleaning data were In this paper, the analysis is carried out using the statistical programming language `R` [@citeR], with the help of extra packages including `arrow` [@arrow], `kableExtra` [@kableExtra], `gridExtra`[@gridExtra], `knitr` [@knitr],   `modelsummary`[@modelsummary], `tidyverse` [@Tidyverse].
 

### 2024-04-19 paper/paper.qmd
added the last references

@@
 A leading expert in gamification and behavioral drive, Yu-kai Chou, has a create framework for gamification called the Octalysis Framework(@fig-framework).Looking at the framework there are eight core drives: Epic Meaning, Accomplishment, Empowerment, Ownership, Social Influence, Scarcity, Unpredictability, and Avoidance.
-For even more in depth explanation, please visit Yu-kai website:https://yukaichou.com/gamification-examples/octalysis-complete-gamification-framework/.
+For even more in depth explanation, please visit Yu-kai website(@yukai).
 
-Let us see how this framework applies to our study, for this example we will using social gamification group, since it one of the better performing groups with game elements.
+Let us see how this framework(@fig-framework) applies to our study, for this example we will using social gamification group, since it one of the better performing groups with game elements.
 Epic Meaning category it is might but some students as they believe if they do well in this course, it could lead to some future goal like their dream job.
@@
 
-Another example that we want to apply this framework is on a popular gamification language learning app, called Duolingo.
+Another example that we want to apply this framework(@fig-framework) is on a popular gamification language learning app, called Duolingo(@Duolingo).
 Duolingo is a free app that has millions of user ranging from public students in third world countries to even Hollywood stars.
-Yu-kai Chou website provides an analysis for Duolingo, which has 6 out of 8 elements of the framework and here I am going to highlight some of the elements.
+Yu-kai Chou website(@yukai) provides an analysis for Duolingo, which has 6 out of 8 elements of the framework and here I am going to highlight some of the elements.
 Firstly, Epic Meaning is to learn a language and the app even asks the user when creating an account what is their purpose for learning new language.
@@
 But there are not many gamification studies that compare treatment to a experiment group, and with open source data to boot.
-Also, Duolingo is popular language learn app, which use gamification and it has millions of active users which suggest that gamification is not a dead field and it is clearly effective for learning languages.
+Also, Duolingo(@Duolingo) is popular language learn app, which use gamification and it has millions of active users which suggest that gamification is not a dead field and it is clearly effective for learning languages.
 
@@
 The Octalysis framework should be used and the design should it is best to meet all 8 core drives.
-Furthermore, Yu-kai is open to collaboration and consulting so that could make the design even better as there is more than just this framework that he talks about on his website.
-In addition, there should focus on social elements as well since that experiement did well in post tests.
+Furthermore, Yu-kai is open to collaboration and consulting so that could make the design even better as there is more than just this framework that he talks about on his website(@yukai).
+In addition, there should focus on social elements as well since that experiment did well in post tests.
 Lastly, this design is probably going to need multiple iterations and constant feedback from the students to further improve it and to allow it eventually surpass the traditional education system.

### 2024-04-19 paper/datasheet_template.qmd
datasheet is completed

@@
 1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
-    - The dataset was created to enable analysis of comparing game-like and social approaches 
+    - The dataset was created to enable analysis of comparing game-like and social approaches to education. The specific task in mind was to determine whether gamifcation was effective or not. 
 2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
-    - TBD
+    - The team who created was unknown and it was created for professors at the University of Alcalá.
 3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
-    - TBD
+    - Not sure entirely, but most likely the University of Alcalá.
 4. *Any other comments?*
@@
 Please provide a description.*
-	- TBD
+	- The dataset is comprised of undergrad students at the University of Alcalá.
+	Specifically, there are marks on assessments.
 2. *How many instances are there in total (of each type, if appropriate)?*
-	- TBD
+	- 379
 3.
@@
 If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
-	- TBD
+	- Yes it contains all students who particapte in this study.
+The larger representatives groups are the students who took this course(Qualification for ICT Users) and even students at University of Alcalá.
 4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
-	- TBD
+	- Each instance in the csv file, consists of a group(control or treatment), age, pretest and post test for certain concepts and final examinations.
 5. *Is there a label or target associated with each instance? If so, please provide a description.*
-	- TBD
+	- It is associated with a student, but out of privacy their name and student id
+	has been removed.
 6.
@@
 This does not include intentionally removed information, but might include, for example, redacted text.*
-	- TBD
+	- 20 students have some missing data, this could be since the data is lost or maybe the student dropped the course.
 7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
-	- TBD
+	- No
 8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
-	- TBD
+	- No
 9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
-	- TBD
+	- Age column has everyone age set to 19, which is average age in the study.
 10.
@@
 Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
-	- TBD
+	- Self-contained and there is official archival versions of this data
+	- https://www.sciencedirect.com/science/article/pii/S2352340917300173.
 11.
@@
 If so, please provide a description.*
-	- TBD
+	- No
 12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
-	- TBD
+	- No
 13.
@@
 If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
-	- TBD
+	- gender is a binary value, make or female.
 14.
@@
 If so, please describe how.*
-	- TBD
+	- No
 15.
@@
 If so, please provide a description.*
-	- TBD
+	- No
 16. *Any other comments?*
-	- TBD
+	- No
 
@@
 If so, please describe how.*
-	- TBD
+	- The data was derive directly from the observable.
 2.
@@
 How were these mechanisms or procedures validated?*
-	- TBD
+	- students from assignments and tests
 3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
-	- TBD
+	- simple random
 4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
-	- TBD
+	- Not sure, I think professors at the University 
 5.
@@
 If not, please describe the timeframe in which the data associated with the instances was created.*
-	- TBD
+	- Took place 2014 and 2015 semesters 
 6.
@@
 If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
-	- TBD
+	- Not sure
 7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
-	- TBD
+	- individuals directly
 8.
@@
 If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
-	- TBD
+	- not sure
 9.
@@
 If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
-	- TBD
+	- not sure
 10.
@@
 If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
-	- TBD
+	- not sure
 11.
@@
 If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
-	- TBD
+	- No
 12. *Any other comments?*
-	- TBD
+	- No
 
@@
 If not, you may skip the remaining questions in this section.*
-	- TBD
+	- Not sure
 2.
@@
 If so, please provide a link or other access point to the "raw" data.*
-	- TBD
+	- Not sure
 3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
-	- TBD
+	- No
 4. *Any other comments?*
-	- TBD
+	- No
 
@@
 1. *Has the dataset been used for any tasks already? If so, please provide a description.*
-	- TBD
+	- Yes, a study "On the effectiveness of game-like and social approaches in learning: Comparing educational gaming, gamification & social networking"
 2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
-	- TBD
+	- https://www.sciencedirect.com/science/article/abs/pii/S0360131515300981
 3. *What (other) tasks could the dataset be used for?*
-	- TBD
+	- Data could be further statistically processed and analyzed.
+	- Further experimental tools can be designed and tested, using this dataset as a benchmark to compare its effectiveness in terms of learning performance.
 4.
@@
 Is there anything a dataset consumer could do to mitigate these risks or harms?*
-	- TBD
+	- No
 5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
-	- TBD
+	- No
 6. *Any other comments?*
-	- TBD
+	- No
 
@@
 If so, please provide a description.*
-	- TBD
+	- Yes, it could be used in replication
 2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
-	- TBD
+	- it is avaiable on ScienceDirect
 3. *When will the dataset be distributed?*
-	- TBD
+	- 2016
 4.
@@
 If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
-	- TBD
+	- Not sure
 5.
@@
 If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
-	- TBD
+	- Not sure
 6.
@@
 If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
-	- TBD
+	- No
 7. *Any other comments?*
-	- TBD
+	- No
 
@@
 1. *Who will be supporting/hosting/maintaining the dataset?*
-	- TBD
+	- SciencDirect Website
 2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
-	- TBD
+	- owner: luis.demarcos@uah.es
 3. *Is there an erratum? If so, please provide a link or other access point.*
-	- TBD
+	- No
 4.
@@
 If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
-	- TBD
+	- Not sure
 5.
@@
 If so, please describe these limits and explain how they will be enforced.*
-	- TBD
+	- Not sure
 6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
-	- TBD
+	- Not sure
 7.
@@
 If so, please provide a description.*
-	- TBD
+	- No
 8. *Any other comments?*
-	- TBD
+	- No
 
